---
title: "Assignment-2"
author: "Harkirat"
date: "July 23, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

### R has built in functions for choose() and factorial(). This task is to write our own variation of the choose() function, that does not use either of these functions. 
### First a function named fact is defined to calculate factorial and then function choose is created that calculates  n! / (( n - r)! * r!).:
### Three test cases are also being used as given below. 
* 1)Testing positive case when 0 <= r <= n
* 2)Testing negative case when r < 0
* 3)Testing negative case when n < r

```{r}
fact <- function(num) {
  # find the factorial of a number
  b <- 1 
  while (num > 0) {
  b <- b * num
  num <- num - 1
  } 
  return(b)
}

choose <- function(n, r) {
 
  if (r < 0) {
    warning("please check if you satisfy condition 0 <= r")
    return(NA)
  }
  if (n < r) {
    warning("please check if you satisfy condition r <= n")
    return(NA)
  } 
    x <- fact(n)
    y <- fact(n - r)
    z <- fact(r)
    result <- x / (y * z)
    return(result)
  }
# Test case 1 - When testing positive case when 0 <= r <= n
test_case_1 <- choose(5, 3)
test_case_1
# Test case 2 - When testing negative case when r < 0
test_case_2 <- choose(5, -3)
test_case_2
# Test case 3 - When testing negative case when n < r
test_case_3 <- choose(3, 5)
test_case_3
```



